---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missingval

<!-- badges: start -->
<!-- badges: end -->

The goal of `missingval` is to provide functions to work with missing values. 

## Installation

You can install the development version of missingval from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/missingval")
```

## Example

This is a basic example which shows you how to count missing values (using `count_all_missing_by_group` function) from the `airquality` dataset by month:

```{r example1}
library(missingval)
## basic example code
count_all_missing_by_group(airquality, Month)
```
The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 

```{r example2}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

